\begin{thebibliography}{9}

\bibitem{schreiner1994}
  A. Schreiner, \emph{Object-Oriented Programming with ANSI-C}, 1994.

\bibitem{kernighan1988}
  B. Kernighan, D. Ritchie, \emph{The C Programming Language (2nd Edition)}, 1988.

\bibitem{bryant2015}
  R. Bryant, D. O’Hallaron, \emph{Computer Systems: A Programmer’s Perspective (3rd Edition)}, 2015.

\bibitem{knuth1997}
  D. Knuth, \emph{The Art of Computer Programming, Volume 1: Fundamental Algorithms (3rd Edition)}, 1997.

\bibitem{dlmalloc}
  D. Lea, \emph{A Memory Allocator (dlmalloc)}, 1987.

\bibitem{slab}
  J. Bonwick, \emph{The Slab Allocator: An Object-Caching Kernel Memory Allocator}, 1994.

\bibitem{knowlton1965}
    K. C. Knowlton, \emph{A Fast Storage Allocator}, Communications of the ACM, Vol. 8, No. 10, pp. 623–625, 1965.

\bibitem{wilson1995}
  P. Wilson, M. Johnstone, M. Neely, D. Bryant, \emph{Dynamic Storage Allocation: A Survey and Critical Review}, 1995.

\bibitem{wilson1998}
  P. Wilson, M. Johnstone, \emph{The Memory Fragmentation Problem: Solved?}, 1998.

\bibitem{puaut2002}
  I. Puaut, \emph{Real-Time Performance of Dynamic Memory Allocation Algorithms}, 2002.

\bibitem{chilimbi2000}
  T. Chilimbi, R. Jones, B. Zorn, \emph{Designing a Trace Format for Heap Allocation Events}, 2000. \\
  \texttt{trishulc@microsoft.com}, \texttt{R.E.Jones@ukc.ac.uk}, \texttt{zorn@microsoft.com}

\bibitem{mtrebi}
  M. Trebi, \emph{Memory Allocators: Implementations and Comparisons}, GitHub Repository, 2020. \\
  \url{https://github.com/mtrebi/memory-allocators}

\bibitem{emeryberger}
  E. Berger, \emph{Malloc Implementations: Historical and Technical Analysis}, GitHub Repository, 2018. \\
  \url{https://github.com/emeryberger/Malloc-Implementations}

\bibitem{epita-malloc}
  \emph{Malloc Tutorial}, École Pour l'Informatique et les Techniques Avancées (EPITA), \\
  \url{https://wiki-prog.infoprepa.epita.fr/images/0/04/Malloc_tutorial.pdf}

\bibitem{anu-malloc}
  \emph{COMP2310: Lab 5 - malloc}, Australian National University, \\
  \url{https://comp.anu.edu.au/courses/comp2310/labs/05-malloc/}

\bibitem{cornell-malloc}
  \emph{CS3410 Project 6: Dynamic Memory Allocation}, Cornell University, 2018. \\
  \url{https://www.cs.cornell.edu/courses/cs3410/2018fa/projects/p6/}

\bibitem{soshnikov-allocator}
  D. Soshnikov, \emph{Writing a Memory Allocator}, 2019. \\
  \url{https://dmitrysoshnikov.com/compilers/writing-a-memory-allocator/}

\bibitem{cvut-dynamic-mem}
  \emph{Dynamic Memory Allocation}, Czech Technical University in Prague (CVUT), \\
  \url{https://cw.fel.cvut.cz/old/_media/courses/a4m33pal/04_dynamic_memory_v6.pdf}

\end{thebibliography}